k-Space Domain Parallel Transmit Pulse Design

### 2020-09-09 Manuscript/Result.tex
wag added W table

\par Table \ref{fig:wsize} lists the size of the final matrix $\bm{W}$ in gigabytes,
versus inclusion width.
As inclusion width increases, more excitation trajectory points are used in the solution of each target location,
until the entire trajectory is used for each point (Inclusion width = $\infty$ in the table),
corresponding to a full solution. 
With the inclusion width of 4 cycles/FOV used here, 
the matrix size was 98\% smaller than that of a full solution.

>>>>

\par Table \ref{fig:wsize} lists the size of the final matrix $\bm{W}$ in gigabytes,
versus inclusion width.
As inclusion width increases, more excitation trajectory points are used in the solution of the weights for each target location,
until the entire trajectory is used for each location (Inclusion width = $\infty$ in the table),
corresponding to a full solution. 
With the inclusion width of 4 cycles/FOV used here, 
the matrix size was 98\% smaller than that of a full solution.
